---
title: "RR_project"
author: "Zixia Zhou/Runan Zhang/Adrianna Świerzak"
date: "2023-06-01"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = TRUE, 
                      cache   = FALSE,
                      message = FALSE, 
                      warning = FALSE)
options(scipen = 10)
install.packages("readxl")
```

## 1.Importing the data

First we load some libraries, function and our data.

```{r cache = FALSE}
library(xts)
library(lmtest)
library(tidyverse)
library(vars)
library(readxl)
library(urca)
```

```{r cache = FALSE}
setwd('/Users/hazelzhou/Desktop/RR')
source("Team-project/functions/testdf.R")
data <- read_excel('Team-project/RR_data.xls')
```

The structure of the data

```{r}
data %>% glimpse()
head(data)
tail(data)
```

Let's correct the type of the `date` variable and transform the `data.frame` into an `xts` object

```{r}
data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
data %>% glimpse()
data <- xts(data[, -1], order.by = data$Date)
```

Next, let's create their difference.

```{r}
data$dEXC <- diff.xts(data$EXC)
data$dINF <- diff.xts(data$INF)
data$dIR <- diff.xts(data$IR)
```

Then, plotting the data.

```{r}
plot(data[, c(1:3)],
     col = c("pink", "lightblue","lightgreen"),
     major.ticks = "months", 
     grid.ticks.on = "months",
     grid.ticks.lty = 3,
     main = "All data",
     legend.loc = "topleft")
```

## 2.Testing cointegration

Cointegration describes a long-term relationship between two or more time series variables. `EXC`, `INF` and `IR` are cointegrated if they are stationary in same difference order and their linear combination is also stationary in lower order.

We will conduct integration order tests on the data. To begin, we will apply the Augmented Dickey-Fuller (ADF) test on the variable `EXC` and its first differences.

```{r}
testdf(variable = data$EXC,
       max.augmentations = 3)
```

As we can see, the p-value of Breusch-Godfrey test, which is used to test for autocorrelation in the residuals is very low in first line.

**H0 = No Autocorrelation**

**Ha = Autocorrelation**

We should reject null hypothesis and we cannot interpret it's ADF test. Even the p-value of BG test is higher than significant level 5%, the p-value of ADF test is higher that significant level 5% in rest of the row, so we should reject the null hypothesis.

Let's interpret the result of first difference.

```{r}
testdf(variable = data$dEXC, 
       max.augmentations = 3)
```

In the first row, it shows higher p-value of BG test and and lower p-value of ADF test. It indicates `EXC` is integrated of order 1.

The paper also conducted the Phillips-Perron (PP) which is similar to ADF. \* $H_0:$ time series is not stationary (integrated of order $\ge 1$) \* $H_a:$ time series is stationary (integrated of order $= 0$)

```{r}
pp.test.EXC <- ur.pp(data$EXC,
                 type = c("Z-tau"), 
                 model = c("constant"))
summary(pp.test.EXC)
```

Value of the test-statistic Z-tau (-0.9295) is higher than the 1% critical value (-3.480998), so we cannot reject the null about non-stationarity of `EXC`.

We will also use PP test for the difference of `EXC`.

```{r}
pp.test.EXC.d <- ur.pp(diff.xts(data$EXC), 
                   type = c("Z-tau"), 
                   model = c("constant"))
summary(pp.test.EXC.d)
```

Value of the test-statistic Z-tau (-6.9487) is now lower than the 1% critical value (-3.481377), so now we **reject** the null about non-stationarity of first differences of `EXC`

By concluding `EXC ~ I(1)`.
