---
title: "Reproduced 'A Vector Error Correction Model (VECM) Approach in Explaining the
  Relationship Between Interest Rate and Inflation Towards Exchange Rate Volatility
  in Malaysia"
author: "Zixia Zhou/Runan Zhang/Adrianna Świerzak"
date: "2023-06-03"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = TRUE, 
                      cache   = FALSE,
                      message = FALSE, 
                      warning = FALSE)
options(scipen = 10)
install.packages("readxl")
```

## 1.Importing the data

To begin, we import the required libraries and define necessary functions. Then, we load our dataset.

```{r cache = FALSE}
library(xts)
library(lmtest)
library(tidyverse)
library(vars)
library(readxl)
library(urca)
```

```{r cache = FALSE}
setwd('/Users/zhangrunan/Desktop')
source("Team-project/functions/testdf.R")
data <- read_excel('Team-project/RR_data.xls')
```

Here is the structure of the data.

```{r}
data %>% glimpse()
head(data)
tail(data)
```

Next, we proceed to correct the data type of the date variable and convert the `data.frame` into an `xts` object. Then we transform the data into log form as the paper mentioned.

```{r}
data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
data %>% glimpse()
data <- xts(data[, -1], order.by = data$Date)
log.data <- log(data)
```

Let's create their difference.

```{r}
log.data$dEXC <- diff.xts(log.data$EXC)
log.data$dINF <- diff.xts(log.data$INF)
log.data$dIR <- diff.xts(log.data$IR)
```

Then, plotting the data.

```{r}
plot(log.data[, c(1:3)],
     col = c("pink", "lightblue","lightgreen"),
     major.ticks = "months", 
     grid.ticks.on = "months",
     grid.ticks.lty = 3,
     main = "log.data",
     legend.loc = "topleft")
```

## 2.Stationarity Test

Stationarity refers to the property of a time series where the statistical properties such as mean, variance, and covariance remain constant over time.

We will apply the Augmented Dickey-Fuller (ADF) test and Phillips-Perron (PP) test on the variable `EXC`, `INF`, `IR` and their first differences.

### 2.1.1 ADF test of `EXC`

First, let's test variable `EXC`.

```{r}
testdf(variable = log.data$EXC,
       max.augmentations = 3)
```

As we can see, the p-value of Breusch-Godfrey test, which is used to test for autocorrelation in the residuals is very low in first line. In such case, the ADF test is inefficient since the residuals are serial correlation.

**H0 = No Autocorrelation**

**Ha = Autocorrelation**

We should reject null hypothesis and we cannot interpret it's ADF test. Even the p-value of BG test is higher than significant level 1%, the p-value of ADF test is higher that significant level 1% in rest of the rows, so we should reject the null hypothesis.

Let's interpret the result of first difference.

```{r}
testdf(variable = log.data$dEXC, 
       max.augmentations = 3)
```

In the first row, it shows higher p-value of BG test and and lower p-value of ADF test. It indicates `EXC` is integrated of order 1.

### 2.1.2 PP test of `EXC`

The paper also conducted the Phillips-Perron (PP) which is similar to ADF.

H0: time series is not stationary

Ha: time series is stationary

```{r}
pp.test.EXC <- ur.pp(log.data$EXC,
                 type = c("Z-tau"), 
                 model = c("constant"))
summary(pp.test.EXC)
```

Test-statistic Z-tau (-1.0015) is higher than the 1% critical value (-3.480998), so we cannot reject the null about non-stationary of `EXC`.

We will also use PP test for the difference of `EXC`.

```{r}
pp.test.EXC.d <- ur.pp(diff.xts(log.data$EXC), 
                   type = c("Z-tau"), 
                   model = c("constant"))
summary(pp.test.EXC.d)
```

Test-statistic Z-tau (-6.9049) is now lower than the 1% critical value (-3.481377), so now we **reject** the null about non-stationary of first differences of `EXC`

By concluding `EXC` \~ I(1)

### 2.2.1 ADF test of `INF`

We are going to repeat the same procedure on variables `INF` and `IR` to see if it is stationary.

```{r}
testdf(variable = log.data$INF,
       max.augmentations = 3)
```

```{r}
testdf(variable = log.data$dINF, 
       max.augmentations = 3)
```

### 2.2.2 PP test of `INF`

```{r}
pp.test.INF <- ur.pp(log.data$INF,
                 type = c("Z-tau"), 
                 model = c("constant"))
summary(pp.test.INF)
```

```{r}
pp.test.INF.d <- ur.pp(diff.xts(log.data$INF), 
                   type = c("Z-tau"), 
                   model = c("constant"))
summary(pp.test.INF.d)
```

After both of the test, variable `INF` \~ I(1). \### 2.3.1 ADF test of `IR`

```{r}
testdf(variable = log.data$IR,
       max.augmentations = 3)
```

```{r}
testdf(variable = log.data$dIR, 
       max.augmentations = 3)
```

### 2.3.2 PP test of `IR`

```{r}
pp.test.IR <- ur.pp(log.data$IR,
                 type = c("Z-tau"), 
                 model = c("constant"))
summary(pp.test.IR)
```

```{r}
pp.test.IR.d <- ur.pp(diff.xts(log.data$IR), 
                   type = c("Z-tau"), 
                   model = c("constant"))
summary(pp.test.IR.d)
```

It is evident that the variable `IR` exhibits stationary in both ADF test and PP test of its levels at significant level of 5%.

## 3.Determination of Lags and Cointegration Test

### 3.1 Determination of Lags

Determining the appropriate number of lags for VECM can be important for accurate analysis. Here we will use the function VARselect.

```{r}
log.data.vecm <- log.data[,c(1:3)]
VARselect(log.data.vecm,
          lag.max = 5)
```

As we could see the lower the value of criteria, the better model. We choose the lag 2.

### 3.2 Cointegration Test

The Johansen test is a statistical procedure utilized to assess whether a group of time series variables exhibit cointegration. Cointegration suggests the existence of a long-term equilibrium relationship among the variables, indicating that they move together in the long run despite short-term fluctuations. It is a foundation of the VECM. Here we will conduct both **Trace test**. **Trace test**

```{r}
johan.test.trace <-
  ca.jo(log.data.vecm,
        ecdet = "const",
        type = "trace",
        K = 2)
summary(johan.test.trace)
```

As the result, we could **Reject** the null hypothesis r=0 at significant level of 10% and cannot reject the null hypothesis r \<= 1 since the test statistic is lower than the critical value. Given that the rank of the Johansen test results is equal to 1, which is greater than zero but less than the number of variables, it indicates that the series are cointegrated. Therefore, we can proceed with estimating the VECM.

## 4. Vector Error Correction Model

```{r}
model <- lm(EXC ~ INF + IR, data = log.data)
summary(model)
```

As the results show, both of the dependent variables are significant since the p-values are lower than significant level 1%. The variable `INF` has negative relationship with `EXC` and `IR` has positive relationship with `EXC`. It states the same finding in the paper. $$ EXC = 0.179788IR - 0.038686INF $$

## 5. Granger Causality test

The Granger causality test is a statistical test used to determine whether one time series variable can predict another time series variable.

```{r}
grangertest(EXC ~ IR,
            data = log.data,
            order = 2)
```

```{r}
grangertest(IR ~ EXC,
            data = log.data,
            order = 2)
```

```{r}
grangertest(EXC ~ INF,
            data = log.data,
            order = 2)
```

```{r}
grangertest(INF ~ EXC,
            data = log.data,
            order = 5)
```

```{r}
grangertest(IR ~ INF,
            data = log.data,
            order = 2)
```

```{r}
grangertest(INF ~ IR,
            data = log.data,
            order = 2)
```

| Null Hypothesis                | Decision      |
|--------------------------------|---------------|
| EXC does not Granger-cause IR  | Do Not Reject |
| IR does not Granger-cause EXC  | Do Not Reject |
| EXC does not Granger-cause INF | Do Not Reject |
| INF does not Granger-cause EXC | Reject        |
| IR does not Granger-cause INF  | Reject        |
| INF does not Granger-cause IR  | Do Not Reject |

We can reach the same conclusion as the article, which is that the relationship between inflation rates and exchange rate fluctuations is unidirectional. Interest rates and exchange rates also exhibit a unidirectional relationship.
