---
title: "Reproduced 'A Vector Error Correction Model (VECM) Approach in Explaining the
  Relationship Between Interest Rate and Inflation Towards Exchange Rate Volatility
  in Malaysia"
author: "Zixia Zhou/Runan Zhang/Adrianna Świerzak"
date: "2023-06-03"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = TRUE, 
                      cache   = FALSE,
                      message = FALSE, 
                      warning = FALSE)
options(scipen = 10)
install.packages("readxl")
```

## 1.Importing the data

To begin, we import the required libraries and define necessary functions. Then, we load our dataset.

```{r cache = FALSE}
library(xts)
library(lmtest)
library(tidyverse)
library(vars)
library(readxl)
library(urca)
```

```{r cache = FALSE}
setwd('/Users/hazelzhou/Desktop/RR')
source("Team-project/functions/testdf.R")
data <- read_excel('Team-project/RR_data.xls')
```

Here is the structure of the data.

```{r}
data %>% glimpse()
head(data)
tail(data)
```

Next, we proceed to correct the data type of the date variable and convert the `data.frame` into an `xts` object. Then we transform the data into log form as the paper mentioned.

```{r}
data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
data %>% glimpse()
data <- xts(data[, -1], order.by = data$Date)
log.data <- log(data)
```

Let's create their difference.

```{r}
log.data$dEXC <- diff.xts(log.data$EXC)
log.data$dINF <- diff.xts(log.data$INF)
log.data$dIR <- diff.xts(log.data$IR)
```
Then, plotting the data.

```{r}
plot(log.data[, c(1:3)],
     col = c("pink", "lightblue","lightgreen"),
     major.ticks = "months", 
     grid.ticks.on = "months",
     grid.ticks.lty = 3,
     main = "log.data",
     legend.loc = "topleft")
```
